Efficient ancestry and mutation simulation with msprime 1.0

### 2021-12-04 paper.tex
Citation for conda-forge
Closes #245

\section*{Availability}
\texttt{Msprime} is freely available under the terms of the
GNU General Public License v3.0, and can be installed from the Python
Package Index (PyPI) or the \texttt{conda-forge} conda channel.
Development is conducted openly on GitHub at
\texttt{https://github.com/tskit-dev/msprime/}.
The documentation for \texttt{msprime} is available at
\texttt{https://tskit.dev/msprime/docs/}.
The source code for all the evaluations and figures in this manuscript
is available at \texttt{https://github.com/tskit-dev/msprime-1.0-paper/}.

>>>>

\section*{Availability}
\texttt{Msprime} is freely available under the terms of the
GNU General Public License v3.0, and can be installed from the Python
Package Index (PyPI) or the \texttt{conda-forge}~\citep{condaforge2015} conda channel.
Development is conducted openly on GitHub at
\texttt{https://github.com/tskit-dev/msprime/}.
The documentation for \texttt{msprime} is available at
\texttt{https://tskit.dev/msprime/docs/}.
The source code for all the evaluations and figures in this manuscript
is available at \texttt{https://github.com/tskit-dev/msprime-1.0-paper/}.
